---
title: "Filling in reporting checklists"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Filling in reporting checklists}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(reportilo)
```

## Getting a checklist

`get_checklist()` (or its alias `new_checklist()`) returns a fillable checklist
for a guideline: one row per item, with an empty `response` column.

```{r}
chk <- get_checklist("prisma-2020")
class(chk)
nrow(chk)
head(chk[, c("item_no", "section", "item_text")])
```

The object carries the guideline id, title and whether the checklist was
hand-verified:

```{r}
attr(chk, "guideline_id")
attr(chk, "verified")
```

## Filling it in

`response` is an ordinary character column. Record the page number (or any note)
where each item is addressed.

```{r}
chk$response[chk$item_no == "1"] <- "p1"
chk$response[chk$item_no == "16a"] <- "p7, Figure 1"

validate_checklist(chk)
```

## Verified versus auto-extracted

The main families ship as hand-verified checklists. Many other guidelines are
auto-extracted from their source documents; treat those as a starting point and
check them against the original. Use `parse_status` to see which is which.

```{r}
ps <- parse_status
head(ps[ps$verified, c("guideline_id", "n_items", "status")])

# guidelines flagged for review (lower-confidence auto-extraction)
sum(ps$needs_review)
```

## Catalog-only guidelines

Guidelines without a machine-readable checklist return `NULL` with a pointer to
their source.

```{r}
catalog_only <- reportilo_guidelines()
catalog_only <- catalog_only$guideline_id[!catalog_only$has_checklist][1]
res <- get_checklist(catalog_only)
is.null(res)
```

For those, `guideline_info()` gives the metadata and source links so you can
work from the original document.

## Exporting

Write the filled checklist to Word, Excel or CSV:

```{r, eval = FALSE}
reportilo_export(chk, "prisma-2020-checklist.docx")
reportilo_export(chk, "prisma-2020-checklist.xlsx")
reportilo_export(chk, "prisma-2020-checklist.csv")
```

See `vignette("export")` for the full list of formats.
