---
title: "Exporting to Word, Excel and images"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exporting to Word, Excel and images}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(reportilo)
```

One function, `reportilo_export()`, writes both checklists and flow diagrams.
The output format comes from the file extension, or from an explicit `format`
argument.

## Supported formats

| Object | Formats |
| --- | --- |
| Checklist (`get_checklist()`) | `docx`, `xlsx`, `csv` |
| Flow diagram (`new_flowchart()`) | `png`, `svg`, `pdf`, `docx`, `xlsx`, `csv` |

For flow diagrams, `xlsx` and `csv` export the counts table; `docx` embeds the
rendered diagram as an image.

## Checklists

```{r, eval = FALSE}
chk <- get_checklist("strobe")
chk$response[1] <- "p3"

reportilo_export(chk, "strobe.docx") # formatted Word table
reportilo_export(chk, "strobe.xlsx") # styled Excel sheet
reportilo_export(chk, "strobe.csv") # plain CSV
```

## Flow diagrams

```{r, eval = FALSE}
fc <- set_counts(new_flowchart("consort_2010"), assessed = 520, randomized = 350)

reportilo_export(fc, "consort.png", width = 1400) # high-resolution PNG
reportilo_export(fc, "consort.svg") # scalable vector
reportilo_export(fc, "consort.pdf") # print-ready PDF
reportilo_export(fc, "consort.docx") # Word with embedded image
```

## Choosing the format explicitly

When the path has no usable extension (for example a temp file), pass `format`:

```{r, eval = FALSE}
tmp <- tempfile()
reportilo_export(chk, tmp, format = "docx")
```

## Optional packages

Exporters load their dependencies only when used, keeping the core install
light:

- Word: `officer` and `flextable`
- Excel: `openxlsx`
- Images: `DiagrammeR`, `DiagrammeRsvg` and `rsvg`

If one is missing, `reportilo_export()` stops with an informative message telling
you what to install.
