---
title: "Building flow diagrams"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Building flow diagrams}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(reportilo)
```

`reportilo` ships three fillable flow diagram templates, all built on one
generic node/edge/count model:

```{r}
flowchart_templates[, c("template_id", "name", "study_type", "n_count_fields")]
```

## Start a diagram

```{r}
fc <- new_flowchart("prisma_2020")
fc
```

## See the fields

Each template exposes a set of fillable fields. Most are numeric counts; some
hold a semicolon-separated list of exclusion reasons.

```{r}
head(flowchart_fields("prisma_2020"), 8)
```

## Fill in the counts

Set fields by name with `set_counts()`. Unknown names raise an error, so typos
are caught early.

```{r}
fc <- set_counts(fc,
  identified_db = 2451,
  duplicates = 320,
  screened = 2034,
  excluded = 1789,
  sought = 245,
  assessed = 237,
  reports_excluded = "Wrong population (n = 120); Wrong outcome (n = 73)",
  studies_included = 42,
  reports_included = 48
)
fc
```

## View it

`render_flowchart()` returns an interactive Graphviz widget.

```{r, eval = requireNamespace("DiagrammeR", quietly = TRUE), fig.width = 7}
render_flowchart(fc)
```

The underlying Graphviz source is available with `flowchart_dot()`, which is
also what the image and Word exporters use.

```{r}
cat(substr(flowchart_dot(fc), 1, 120), "...")
```

## Export

```{r, eval = FALSE}
reportilo_export(fc, "prisma-flow.png") # also svg, pdf
reportilo_export(fc, "prisma-flow.docx") # embedded image
reportilo_export(fc, "prisma-counts.xlsx") # the counts as a table
```

## The CONSORT and STARD templates

`"consort_2010"` is a two-arm parallel trial diagram and `"stard_2015"` is a
diagnostic accuracy flow. They are filled the same way; use
`flowchart_fields()` to discover their fields.

```{r}
nrow(flowchart_fields("consort_2010"))
nrow(flowchart_fields("stard_2015"))
```
