---
title: "Getting started with reportilo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with reportilo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(reportilo)
```

`reportilo` turns the [EQUATOR Network](https://www.equator-network.org/)
library of reporting guidelines into a working toolkit. The workflow is three
steps: **find** a guideline, **fill** its checklist or flow diagram, and
**export** the result.

## Find

Browse or search the catalog of reporting guidelines.

```{r}
# the whole catalog
nrow(reportilo_guidelines())

# only guidelines that ship a fillable checklist
nrow(reportilo_guidelines(checklist_only = TRUE))

# search across acronym, title, study design and clinical area
head(search_guidelines("randomised trial"), 5)
```

Look up one guideline (by `guideline_id` or an unambiguous acronym):

```{r}
guideline_info("prisma-2020")
```

## Fill

Get a fillable checklist. Each row is one item; record where you address it in
the `response` column.

```{r}
chk <- get_checklist("strobe")
head(chk)

chk$response[1:3] <- c("p1", "p2", "p2")
validate_checklist(chk)
```

Flow diagrams work the same way. Start from a template, set the counts, and
view it.

```{r}
fc <- new_flowchart("prisma_2020")
fc <- set_counts(fc, identified_db = 1200, screened = 980, excluded = 700)
fc
```

```{r, eval = requireNamespace("DiagrammeR", quietly = TRUE), fig.width = 6}
render_flowchart(fc)
```

## Export

Write either object to Word, Excel or an image. The format follows the file
extension.

```{r, eval = FALSE}
reportilo_export(chk, "strobe-checklist.docx")
reportilo_export(chk, "strobe-checklist.xlsx")
reportilo_export(fc, "prisma-flow.png")
```

## Three front ends

The same data and logic power three interfaces:

- the **R package** documented here;
- a bundled **Shiny app**, `launch_reportilo()`; and
- a **browser app** at <https://choxos.github.io/reportilo/app/>.

## Data coverage and provenance

For v0.1.0 the main families (such as PRISMA 2020, CONSORT 2010 and STROBE) ship
as hand-verified checklists. Other guidelines are best-effort auto-extracted
from their source documents, and the rest are catalog entries that link to the
original. The `parse_status` dataset records the coverage and confidence for
every guideline.

```{r}
table(parse_status$status)
```
